---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 10"
author: "Eric Weah"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 10 Exercises: 10.1-10.9

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)
library(ggplot2)

```



## Chapter 10 Exercises

### Problem 10.1
1.) Summary 
2.) Data verb
3.) reduction 
4.) reduction 
5.) summary 
6.) Summary 
7.) Data verb
8.) Summary 

### Problem 10.2
1.) mutate() fucntion
2.) Arrange() function
3.) filter() function
4.) select() function
5.) select() fucntion 
### Problem 10.5
1.) First we will use the 'filter()' function to show cases with first and second, then we can use the 'n()' function to count the cases who picked the same candidate for first and second
```{r}
Minneapolis2013 %>%
  filter(First==Second)%>%
  summarise(n())



```
2.) For this problem, we use filter() function to make sure first and second are the same.after that we can use group_by() with first and second to find how many of each pair. The summarise(total = n()) will find the number of each pair. arrange() will order by decreasing order. head(4) will include the undervote.
```{r}
Minneapolis2013 %>%
  group_by(First,Second)%>%
  filter(First==Second)%>%
  summarise(total=n())%>%
  arrange(desc(total))%>%
  head(4)
```

3.) For this problem we firdt use group_by() to group the first and second. The filter() fucntion with the argument will filter pairs with ole savior. We can then use the summarise() fucntion with its argument to find the number of distinct pair. The arrange() fucntion  with its argument to arrange the results in decreasing total. the Head(4) will display the top 3 second and first choices of ole savior.
```{r}
Minneapolis2013 %>%
  group_by(First, Second) %>%
  filter(First=="OLE SAVIOR") %>%
  summarise(total=n()) %>%
  arrange(desc(total)) %>%
  head(4)
  
```


### problem 10.6
1.)
```{r}
diamonds %>% group_by(color) %>% summarise(avg = mean(carat)) %>% arrange(desc(avg)) %>% head(1)


```
verb1= group_by  args1= color
    verb2= summarise args2= avg= mean(carat)
    args3= avg
2.)

```{r}
diamonds %>% group_by(color) %>% summarise(Tables = mean(table/carat)) %>% arrange(desc(Tables)) %>% head(1)

```
verb1= group_by  args1= color
    verb2= summarise args2= tables = mean(table/carat)
    args3= tables
    
### Problem
